\documentclass[11pt]{article}

\begin{document}
\begin{thebibliography}{9}

\bibitem{Irwin2009A-preliminary-m}
J.~Irwin, M.~Torres-Urquidy, T.~Schleyer, and V.~Monaco.
\newblock A preliminary model of work during initial examination and treatment
  planning appointments.
\newblock {\em Br Dent J}, 206(1):E1, Jan 10 2009.


\bibitem{Bargeron2003Reflowing-digit}
D.~Bargeron and T.~Moscovich.
\newblock Reflowing digital ink annotations.
\newblock In {\em Proceedings of the SIGCHI conference on Human factors in
  computing systems}, pages 385--93, New York, NY, 2003. ACM.

\bibitem{Beinlich1993Pen-based-remot}
I.~Beinlich, C.~Bokemeyer, U.~R{\"a}th, R.~Walter-Kirst, J.~Hartlapp,
  J.~Muschiol, U.~Fraass, and H.~Schneider.
\newblock Pen-based remote data entry system. a pilot clinical trial.
\newblock {\em Arzneimittel-Forschung}, 43(3):399--404, 1993.

\bibitem{Cole2006A-comparative-s}
E.~Cole, E.~Pisano, G.~Clary, D.~Zeng, M.~Koomen, C.~Kuzmiak, B.~Seo, Y.~Lee,
  and D.~Pavic.
\newblock A comparative study of mobile electronic data entry systems for
  clinical trials data collectio.
\newblock {\em Int J Med Inform}, 75(10-11):722--29, 2006.

\bibitem{Haller2009Handheld-vs.-la}
G.~Haller, D.~Haller, D.~Courvoisier, and C.~Lovis.
\newblock Handheld vs. laptop computers for electronic data collection in
  clinical research: a crossover randomized trial.
\newblock {\em J Am Med Inform Assoc}, 16(5):651--59, Sep-Oct 2009.

\bibitem{Karunakaran2012Investigating-b}
A.~Karunakaran, Y.~Hee-Nam, and M.~Reddy.
\newblock Investigating barriers to electronic medical record use during
  collaborative information seeking activities.
\newblock In {\em Proceedings of the 2nd ACM SIGHIT symposium on International
  health informatics}, IHI '12, pages 743--48, New York, NY, 2012. ACM.

\bibitem{Kirby1996The-PEN--PAD-da}
J.~Kirby and A.~Rector.
\newblock The pen \& pad data entry system: from prototype to practical system.
\newblock {\em Proc Annu Symp Am Med Inform Assoc}, page 709, 1996.

\bibitem{Mackenzi2002Text-entry-for-}
S.~Mackenzi and W.~Soukoreff.
\newblock Text entry for mobile computing: models and methods, theory and
  practice.
\newblock {\em Human-Computer Interaction}, 17(2 and 3):147--98, 2002.

\bibitem{Mayrhofer2007Pen-based-Elect}
D.~Mayrhofer.
\newblock Pen-based electronic medical record on a tablet pc in a medical
  practice.
\newblock Masters thesis, Vienna University of Technology, 2007.

\bibitem{Moorman1994A-model-for-str}
P.~Moorman, A.~Van~Ginneken, J.~van~der Lei, and J.~van Bemmel.
\newblock A model for structured data entry based on explicit descriptional
  knowledge.
\newblock {\em Methods Inform Med}, 33(5):454--63, 1994.

\bibitem{Ramos2007Pointing-lenses}
G.~Ramos, A.~Cockburn, R.~Balakrishnan, and M.~Beaudouin-Lafon.
\newblock Pointing lenses: facilitating stylus input through visual-and
  motor-space magnification.
\newblock In {\em Proceedings of the SIGCHI conference on Human factors in
  computing systems}, CHI '07, pages 757--66, New York, NY, 2007. ACM.

\bibitem{Rosenbloom2006Interface-Termm}
S.~Rosenbloom, R.~Miller, K.~Johnson, P.~Elkin, and S.~Brown.
\newblock Interface termminologies: Facilitating direct entry of clinical data
  into electronic health record systems.
\newblock {\em J Am Med Inform Assoc}, 13(3):277--288, May-Jun 2006.

\bibitem{Seneviratne2010Improving-stylu}
N.~Seneviratne and B.~Plimmer.
\newblock Improving stylus interaction for emedical forms.
\newblock In {\em Proceedings of the 22nd Conference of the Computer-Human
  Interaction Special Interest Group of Australia on Computer-Human
  Interaction}, OZCHI '10, pages 280--87, New York, NY, 2010. ACM.

\bibitem{Sudano2005Using-tablet-PC}
J.~Sudano, B.~Kofford, and S.~Wotman.
\newblock Using tablet pc's in dental practice research: technology, cost
  savings, and direct data entry "on the go".
\newblock {\em J Public Health Dent}, 65(4):244--5, Fall 2005.

\bibitem{Taib2006Multimodal-User}
R.~Taib, Y.~Shi, E.~Choi, F.~Chen, M.~Sladescu, and N.~Phung.
\newblock Multimodal user interface facilitating critical data entry for
  traffic incident management.
\newblock In {\em Proceedings of the 2005 NICTA-HCSNet Multimodal User
  Interaction Workshop}, volume~57 of {\em MMUI '05}, pages 55--9,
  Darlinghurst, Australia, 2006. Austrailian Computer Society, Inc.

\bibitem{Mulligen1998Clinical-data-e}
E.~van Mulligen, H.~Stam, and A.~Van~Ginneken.
\newblock Clinical data entry.
\newblock {\em Proc Annu Symp Am Med Inform Assoc}, page~81, 1998.

\bibitem{Nygren1992Reading-the-med}
E.~Nygren and P.~Henriksson.
\newblock Reading the medical record. analysis of physicians' ways of reading
  the medical record.
\newblock {\em Comput Methods Programs Biomed}, 39(1-2):1--12,
  September-October 1992.

\bibitem{Shachak2009Primary-care-ph}
A.~Shachak, M.~Hadas-Dayagi, A.~Ziv, and S.~Reis.
\newblock Primary care physicians' use of an electronic medical record system:
  a cognitive task analysis.
\newblock {\em J Gen Intern Med}, 24(3):341--8, March 2009.



\end{thebibliography}
\end{document}